---
output:
  md_document:
    variant: markdown_github
---

This is a direct replication of the code from [Karthik Ram's `wesanderson` palette](https://github.com/karthik/wesanderson) and [David Miller's `beyonce` palette](https://github.com/dill/beyonce)

But, I generated Colour Palettes using the wonderful and inspirational palettes from [colourlisa.com](http://www.colourlisa.com/)

## Installation

```R
devtools::install_github("skiptoniam/artists")
```

## Usage

```{r, palettes_dummy}
library(artists)
```

```{r, all_palettes, fig.width=8, fig.height=26}
par(mfrow=c(26,5))
for(i in 1:128) print(artist_palette(i))
```

My only slight tweek is an abilitiy to view the art work your colour palette is based on.
This can be achieved by setting `see_painting = TRUE`

This is one of my favorites
```{r,fig.width=10, fig.height=6}
par(mfrow=c(1,2))
artist_palette(1,see_painting = TRUE)
library(jpeg)
jj <- readJPEG('./a.jpg',native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)
```
