---
output:
  md_document:
    variant: markdown_github
---

This is a direct replication of the code from [Karthik Ram's `wesanderson` palette](https://github.com/karthik/wesanderson) and [David Miller's `beyonce` palette](https://github.com/dill/beyonce)

But, I generated Colour Palettes using the wonderful and inspirational palettes from [colorlisa.com](http://www.colorlisa.com/)

## Installation

```R
devtools::install_github("skiptoniam/artists")
```

## Usage

```{r, palettes_dummy}
library(artists)
```

Here is a complete list of artworks and their colour palettes.
```{r, all_palettes, fig.width=12, fig.height=26,message=FALSE,warning=FALSE,error=FALSE,results='hide'}
par(mfrow=c(26,5))
for(i in 1:128) print(artist_palette(i))
```

My only slight tweek is an abilitiy to view the art work your colour palette is based on.
This can be achieved by setting `see_painting = TRUE`

This is one of my favorites
```{r, luminous_day_josef_albers,fig.width=10, fig.height=10}
par(mfrow=c(2,1))
artist_palette(1,see_painting = TRUE)
library(jpeg)
jj <- readJPEG('./a.jpg',native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)
```

```{r}
library(ggplot2)
df <- data.frame(
  x = runif(100),
  y = runif(100),
  z1 = rnorm(100),
  z2 = abs(rnorm(100))
)
ggplot(df, aes(x, y)) +
  geom_point(aes(colour = z1,size=z2)) +
  scale_colour_gradientn(colours = artist_palette(1,100,type ='continuous'))  

```

I also really like this one too. Which seems to make nice plots.
```{r, golden_cloud_gretchen_albrecht,fig.width=8, fig.height=10}
par(mfrow=c(2,1))
artist_palette(3)
library(jpeg)
jj <- readJPEG('./b.jpg',native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)
```

Here is an example of using this colour palette in `ggplot`.
```{r, diamonds_w_golden_cloud,fig.width=8, fig.height=6}
library(ggplot2)
ggplot(diamonds, aes(x = price, fill = cut)) +
  geom_histogram(position = "dodge", binwidth = 1000)+
  scale_fill_manual(values = artist_palette(3))

```

Bauhaus Stairway by Oskar Schlemmer is awesome for heat maps.
```{r,Bauhaustreppe,fig.width=8, fig.height=6}
cols <- artist_palette(104,100,type ='continuous')
ggplot(faithfuld, aes(waiting, eruptions)) +
     geom_raster(aes(fill = density))+
     scale_fill_gradientn(colours = cols) 
```

