---
output:
  md_document:
    variant: markdown_github
---

This is a direct replication of the code from [Karthik Ram's `wesanderson` palette](https://github.com/karthik/wesanderson) and [David Miller's `beyonce` palette](https://github.com/dill/beyonce)

But, I generated Colour Palettes using the wonderful and inspirational palettes from [colorlisa.com](http://www.colorlisa.com/)

## Installation

```R
devtools::install_github("skiptoniam/artists")
```

## Usage

```{r, palettes_dummy}
library(artists)
```

Here is a complete list of artworks and their colour palettes.
```{r, all_palettes, fig.width=12, fig.height=26,message=FALSE,warning=FALSE,error=FALSE}
par(mfrow=c(26,5))
for(i in 1:128) print(artist_palette(i))
```

My only slight tweek is an abilitiy to view the art work your colour palette is based on.
This can be achieved by setting `see_painting = TRUE`

This is one of my favorites
```{r, luminous_day_josef_albers,fig.width=10, fig.height=10}
par(mfrow=c(2,1))
artist_palette(1,see_painting = TRUE)
library(jpeg)
jj <- readJPEG('./a.jpg',native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)
```

I also really like this one too. Which seems to make nice plots.
```{r, golden_cloud_gretchen_albrecht,fig.width=8, fig.height=10}
par(mfrow=c(2,1))
artist_palette(3)
library(jpeg)
jj <- readJPEG('./b.jpg',native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)
```

Here is an example of using this colour palette in `ggplot`.

```{r, diamonds_w_golden_cloud,fig.width=8, fig.height=6}
library(ggplot2)
ggplot(diamonds, aes(x = price, fill = cut)) +
  geom_histogram(position = "dodge", binwidth = 1000)+
  scale_fill_manual(values = artist_palette(3))

```
